Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
Update manuscript.Rmd

The Fogo Island archipelago, off the coast of Newfoundland, Canada,
is home to approximately 300 woodland caribou. During routine fieldwork on May
30, 2017, we observed an unmarked adult male caribou swim between Wester and
Eastern Indian Islands (Figure 1), a swim of at least 470 m which took ~9
minutes (~52 m per minute). This observation prompted us to investigate whether
swimming behaviour was common among GPS radio-collared caribou in the population
(n = 29 adult females: 1240g, GPS 4400M; Lotek Wireless Inc., Newmarket,
Ontario, Canada). We identified swimming events when two consecutive GPS (2-hour
relocation rates) locations from an individual occurred on different islands.
This region typically experiences pack ice during the winter, so caribou may be
able to travel between islands by walking over the ice. We restricted our GPS
data to the ice-free period of the year (April 1 - November 25) and we
identified three adult female caribou that collectively engaged in 86 swimming
events (Figure 2).

In total, 
<!--Is it better to just state our results here, or give this sort of teaser? Initially I had "86 events by 3 individuals" here, but then we ignore that for a couple paragraphs of context before getting back into it... which seemed weird-->

@@

Fogo Island is the largest island in the archipelago (237.71 km^2^), but there
are at least three other large islands: Western Indian (77.6 km2), Eastern
Indian (38.7 km2) and Change (XX km2) Islands, as well as numerous smaller
islands, including Blundon’s (1.18 km2), North Long (1.01 km2), South Long (0.48
km2), Kate’s (1.64 km2), and Brother’s (1.59 km2) Islands (see Figure 1).
Habitats are similar across the archipelago, consisting largely of coniferous
and mixed forests of balsam fir (*Abies balsamea*), black spruce (*Picea
mariana*), and white birch (*Betula papyrifera*) as well as bogs, lakes, lichen
and rocky barrens.

>>>>

The Fogo Island archipelago, off the coast of Newfoundland, Canada,
is home to approximately 300 woodland caribou. During routine fieldwork on May
30, 2017, we observed an unmarked adult male caribou swim between Wester and
Eastern Indian Islands (Figure 1), a swim of at least 470 m which took ~9
minutes (~52 m per minute). This observation prompted us to investigate whether
swimming behaviour was common among GPS radio-collared caribou in the population
(n = 29 adult females: 1240g, GPS 4400M; Lotek Wireless Inc., Newmarket,
Ontario, Canada). We identified swimming events when two consecutive GPS (2-hour
relocation rates) locations from an individual occurred on different islands.
This region typically experiences pack ice during the winter, so caribou may be
able to travel between islands by walking over the ice. We restricted our GPS
data to the ice-free period of the year (April 1 - November 25) and we
identified three adult female caribou that collectively had 86 swimming
events (Figure 2).

In total, these 86 swimming events occured in month (n = Y), month (n = Y), and
month (n = Y), while the remaining events were in month, month, and month (n =
Y). On average, caribou swam between islands approximately ever 24 days, but
some individuals swam up to XX times per week/month/whatever. <!--Is it better
to just state our results here, or give this sort of teaser? Initially I had "86
events by 3 individuals" here, but then we ignore that for a couple paragraphs
of context before getting back into it... which seemed weird-->

@@

<!-- still not sure we need this paragraph, I wonder if the island size
information could be included in the figure caption?--> Fogo Island is the
largest island in the archipelago (237.71 km^2^), but there are at least three
other large islands: Western Indian (77.6 km2), Eastern Indian (38.7 km2) and
Change (XX km2) Islands, as well as numerous smaller islands, including
Blundon’s (1.18 km2), North Long (1.01 km2), South Long (0.48 km2), Kate’s (1.64
km2), and Brother’s (1.59 km2) Islands (see Figure 1). Habitats are similar
across the archipelago, consisting largely of coniferous and mixed forests of
balsam fir (*Abies balsamea*), black spruce (*Picea mariana*), and white birch
(*Betula papyrifera*) as well as bogs, lakes, lichen and rocky barrens.
